### 2013-04-22 5/applications.tex
added 201304_Apr22

@@

@@

SAR is stochastic and SAR speckle filtering is the removal of stochastic ``noise''.
The principle of many speckle filters in removing stochastic noise is to group data into homogeneous areas.
In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$n$ is the total number of pixel in the surrounding areas.
The implicit assumption is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
%Clearly, in real-life images, the assumption in boxcar filter is too easy to get violated.
In a filter previously proposed by the authors \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is given in Eqn. \ref{eqn:kmle},
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$k$ is the total number of pixels in the partitioned and homogeneous area covering the centre point.

By and large, while it appears logical to classify surrounding pixels as being either in the same homogeneous area with the central point or not,
  the concept of ``homogeneous area'' lacks precise definition and boundaries.
This is self-evident in the need for a threshold on the variance measured to assert homogeneity in an ensemble of stochastic samples.

This paper presents a different approach, that of fuzzy logic.
Fuzzy logic embraces truth values that range from 1 to 0, 
	instead of fixing on a rigid two-member set of logical values (i.e. true and false).
Thus instead of making an YES/NO decision on whether or not a data point is in the same homogeneous region with the estimating central point, a fuzzy probabilistic scale is calculated.
Then the noise-removal impact of the surrounding data point will be scaled with this possibilistic probability, in contrast to the usual scheme that proceeds with ``full impact'' or ``no impact at all''.

The idea presented in this paper is structured as follows:
Section \ref{sec:fmle_estimation} will describe the FMLE estimation in details.
The performance of the proposed filter will be evaluated in Section \ref{sec:results_eval}.
Finally, Section \ref{sec:conclusion} concludes this paper.
%The last section will offers some conclusion and finalizes the paper.

The foundation of the approach is the consistent sense of distance found in the log-transformed domain.
It is shown in \cite{Le_2010_ACRS} that given two SAR intensity samples coming from the same background, their distance in the log transformed domain follows a fixed distribution.

Log transformation is defined as:
${L_I}^i = \log_2{(I^i)}$ 
where 
	$I^i$ is the \textit{$i^{th}$} intensity sample in the originally measured domain,
	$L_I^I$ is the value of that sample in the log-transformed domain.
%Distance in log-transformed domain is defined as:
Log domain distance is defined as:
$D= L_I^1 - L_I^2$. 
Assumming $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
  then distance will follow the distribution 
$pdf(D)= \frac{2^D}{(1+2^D)^2} \ln2$,
  which is consistent.
The analysis is confirmed by real-life data validations (see \cite{Le_2010_ACRS}) and visually demonstrated in Fig. \ref{fig:consistent_contrast_log_domain}.

@@

Using a fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the center point $I_0$ has a likelihood of being in the same homogeneous area given as: 
$p_i = pdf(D_i)$, with $D_i=log_2(I_i) - log_2(I_0)$.
We then propose a new approximation given in Eqn. \ref{eqn:fmle_incl}

%We will see how this works in an homogeneous simulated area.
%The figures demonstrate speckle being filtering effects.
In implementating this estimator, we noticed there are visible black dots in the filtered image.
These dots can be explained as the long-tailed nature of the intensity PDF, 
  which manifests itself in the significant existence of very small values in the population.
In the all-inclusive scheme, this will results in 
	a single $D_0=0$ (at $I_0$) and other very large $D_{i, (i > 0)}$, hence
	a single significant $p_0$ (at $I_0$), and other probably insignificant $p_{i, (i>0)}$.
This marginalises the filtering power of surrounding pixels.
An option is to exclude the centre point $I_0$ from its estimation (see Eqn. \ref{eqn:fmle_excl})

@@

%\subsection{Comparing the two schemes}
Both filters are applied to an simulated single-look homogeneous scene 
and the histogram of the filtered images are plotted in Fig. \ref{fig:compare_filters_histograms:Original} and Fig. \ref{fig:compare_filters_distance_histograms:Original}.
The filtering power is clearly visible.
%demonstrated in Figure \ref{fig:compare_filters_histograms:Original}. 
In comparing the two schemes' histogram in the same figure, it appears that 
	the filtering power of ignoring centre point scheme is at least as powerful as that of centre point included scheme and
	the skewness in the histogram of the ignoring scheme is also appearing less than that of the included scheme.

@@

\subsubsection{Preservation of Distance Histogram Consistency}

Fig. \ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the distance histograms found in the outputs of applying FMLE filters on the inputs depicted in Fig. \ref{fig:compare_filters_histograms:Original}.
They clearly demonstrate that the filtering treatment described above preserves the consistent sense of distance.
This can be explained from the consistent histogram of the fuzzy possbilistic probabilities.
Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves large number of random variables.
This renders the task of giving analytical PDF impractical.
However, large scale computer simulations can provide a practical histogram, from which the PDF can estimated.
%from large scale simulations. 
%Simulating experiments with $10^6$ samples is carried out and the histogram information is saved.
Given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by intrapolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.

@@

The preservation of consistent distance property is the enabling factor that allows the recursive use of FMLE filters.
Additional applications of the filtering process can be expected to reduce the random noise variance even further.
In a sense, this scheme is similar to statistical asymptotic estimations, with the added advantage of spatial preservation.

In the subsequent application of the filtering algorithm, the main different when compared with the filters in initial iteration is the way the new fuzzy probabilities being calculated.
This subsequent computation of fuzzy probabilities is based on the derived distance PDF, being computed in the previous section.
This process is iterated iteratively, with the histogram obtained from the previous iteration serves as probabilistic distance PDF input of the subsequent application of the filter.
This scheme allows speckle to be further depressed, as illustrated in Fig. \ref{fig:plot_incl_distance_pdf_by_iterations}

\begin{figure}[h!]
\centering
	\subfloat[FMLE (incl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.123}
	}
	\subfloat[FMLE (incl): 456]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.345}
	} 
	\subfloat[FMLE (excl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.123}
	}
	\subfloat[FMLE (excl): 456]{          
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.345}
	}
\caption{Iteratively Improving in Distance Histograms}
\label{fig:plot_incl_distance_pdf_by_iterations}
\end{figure}

The log-transformed domain provides a consistent sense of distance.
By embracing a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes use of this consistency.
Experimental results suggest that the estimator's output also exhibits this consistency property, which allows recursive application of the filter discussed above.
The performance of the filter is evaluated both qualitatively against real images and quantitatively via simulated experiments.
The speckle suppression power is evaluated by measuring the ubiquitous MSE on simulated and perfectly homogeneous truth-grounded experiments.
The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available scene and computational power, is sufficiently large.
For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as statistical evidence for better performance in the subsequent tasks of target detection and surface classification.
Experiments confirm the power of FMLE filters in various heterogeneously simulated areas.
They also exhibit good correlation between the MSE and the AUC index.

@@

Estimators are evaluated based on the bias and variance properties of their estimates. 
The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. 
Due to the stochastic nature of simulation process, results of repeated experiments are normally preferred.

@@

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
%Estimators are typically evaluated based on the bias and variance properties of their estimates: 
%	with lower bias and / or lower variance, hence lower MSE indicates better accuracy.
Estimators are typically evaluated based on the bias and variance properties of their estimates:
  lower bias and/or lower variance would lead to lower MSE, which then indicates better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
In addition, due to the stochastic nature of SAR-processing, and thus its simulating process, 
	statistical summaries of repeatedly-simulated experiments are normally preferred to single-run results.

@@

\subsubsection{ Estimating ENL from MSE index in homogeneous areas }
\label{sec:homogeneous_theoretical}

>>>>

%SAR is stochastic and SAR speckle filtering is the removal of stochastic ``noise''.
The principle of many speckle filters in removing the stochastic noise is to group data into homogeneous areas.
In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$n$ is the total number of pixel in the surrounding areas.
The implicit assumption is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
%Clearly, in real-life images, the assumption in boxcar filter is too easy to get violated.
%In a filter previously proposed by the authors
In the kMLE filter presented above and in \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is given in Eqn. \ref{eqn:kmle},
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$k$ is the total number of pixels in the partitioned and homogeneous area covering the centre point.

@@

%By and large,
While it appears logical to classify surrounding pixels as being either in the same homogeneous area with the central point or not,
  the concept of ``homogeneous area'' lacks precise definition and boundaries.
%This is self-evident in the need for a threshold on the variance measured to assert homogeneity in an ensemble of stochastic samples.
In fact, the classification decisions between homogeneity and heterogeneity are probabilistic in nature.
%the concept of “homogeneous area” lacks precise definition and boundaries. 
This is evident in the statistical hypothesis testing used to support these decision makings.

The fMLE speckle filter presented in this section follow fuzzy logic approach,
  which, instead of fixing on a rigid two-member set of logical values (i.e. true and false),
  embraces truth values that range from 1 to 0.
Thus instead of making an YES/NO decision on whether or not a data point is in the same homogeneous region with the estimating central point, a fuzzy probabilistic scale is calculated.
Then the noise-removal impact of the surrounding data point will be scaled with this possibilistic probability,
  in comparison to the usual scheme that proceeds with ``full impact'' or ``no impact at all''.
The benefit of this fuzzy logic approach is that: we no longer need to worry about the homogeneous / heterogeneous problem.

%The idea presented in this paper is structured as follows:
%Section \ref{sec:fmle_estimation} will describe the FMLE estimation in details.
%The performance of the proposed filter will be evaluated in Section \ref{sec:results_eval}.
%Finally, Section \ref{sec:conclusion} concludes this paper.
%The last section will offers some conclusion and finalizes the paper.

@@

The foundation of the fuzzy-estimation approach is the consistent sense of distance found in the log-transformed domain.
%It is shown in \cite{Le_2010_ACRS}
The consistent sense of distance states that given two SAR intensity samples coming from the same background, their distance in the log transformed domain follows a fixed distribution.

The base-2 log transformation is defined as:
${L_I}^i = \log_2{(I^i)}$ 
where 
	$I^i$ is the \textit{$i^{th}$} intensity sample in the originally measured domain,
	$L_I^I$ is the value of that sample in the log-transformed domain.
%Distance in log-transformed domain is defined as:
The log-contrast is then defined as:
$D= L_I^1 - L_I^2$. 
Assumming $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
  then this dis-similarity distance will follow the distribution 
$pdf(D)= \frac{2^D}{(1+2^D)^2} \ln2$,
  which is consistent.
This analysis is confirmed by real-life data validations (see \cite{Le_2010_ACRS}) and visually demonstrated in Fig. \ref{fig:consistent_contrast_log_domain}.

@@

In this fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the center point $I_0$ has a likelihood of being in the same homogeneous area given as: 
$p_i = pdf(D_i)$, with $D_i=log_2(I_i) - log_2(I_0)$.
The fMLE approximation is then proposed as written in Eqn. \ref{eqn:fmle_incl}.

%We will see how this works in an homogeneous simulated area.
%The figures demonstrate speckle being filtering effects.
In implementing this statistical estimator, there are very noticable black dots in the filtered output image.
These dots can be explained as the long-tailed nature of the intensity PDF, 
  which manifests itself in the significant existence of very small values in the population.
In this all-inclusive scheme, there is 
	a single $D_0=0$ (at $I_0$) in the middle of other very large $D_{i, (i > 0)}$, which results in
	a single significant $p_0$ (at $I_0$), and other probably insignificant $p_{i, (i>0)}$.
This marginalises the filtering power of surrounding pixels.
One way to counter this effect is to exclude the centre point $I_0$ from its estimation,
  which results in the exclusive scheme written in Eqn. \ref{eqn:fmle_excl}.

@@

%\subsection{Comparing the two schemes}
For visualization and comparison purposes, both filtering schemes are applied to an simulated single-look homogeneous scene 
and the histogram of the filtered images are plotted in Fig. \ref{fig:compare_filters_histograms:Original} and Fig. \ref{fig:compare_filters_distance_histograms:Original}.
The speckle suppression power is clearly visible.
%demonstrated in Figure \ref{fig:compare_filters_histograms:Original}.
For comparison, the two schemes’ histogram are plotted in the same figure.
%In comparing the two schemes' histogram in the same figure,
And it is apparent that 
	the filtering power of ignoring centre point scheme is at least as powerful as that of centre point included scheme and
	the skewness in the histogram of the exclusive scheme is less than that of the inclusive estimation.

@@

\subsubsection{Preservation of Log-Distance Histogram Consistency}

Fig. \ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the filtering treatment described above being applied on the inputs depicted in Fig. \ref{fig:compare_filters_histograms:Original}.
They clearly demonstrate that the FMLE speckle filters preserves the consistent sense of distance.
This can be explained from the consistent histogram of the input log distance PDF.

Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves large number of random variables.
This renders the task of giving analytical PDF for the output log-distance impractical.
However, large scale computer simulations can be used to provide an usable histogram, from which a PDF can estimated.
%from large scale simulations. 
%Simulating experiments with $10^6$ samples is carried out and the histogram information is saved.
Specifically, given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by intrapolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.

@@

The preservation of consistent distance property is the enabling factor that allows the recursive application of FMLE filters.
Additional execution of the filtering process is be expected to further reduce the random noise power / variance even further.
%In a sense, this scheme is similar to statistical asymptotic estimations, with the added advantage of spatial preservation.

In subsequent application of the filtering algorithm, the main different when compared with the initial iteration is the way the new fuzzy probabilities being calculated.
This subsequent computation of fuzzy probabilities is based on the output distance PDF, whose computation process is described in the previous section.
This process is repeated iteratively, with the histogram obtained from the previous iteration serves as the input fuzzy probability PDF in subsequent application of the filter.
%This scheme allows speckle to be further depressed, as illustrated in
Fig. \ref{fig:plot_incl_distance_pdf_by_iterations} illustrates the extra speckle suppression power of this scheme.

\begin{figure}[H]
\centering
	\subfloat[FMLE (incl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.123}
	}
	\subfloat[FMLE (incl): 456]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.345}
	} 
	\subfloat[FMLE (excl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.123}
	}
	\subfloat[FMLE (excl): 456]{          
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.345}
	}
\caption{Iteratively Improving in Distance Histograms}
\label{fig:plot_incl_distance_pdf_by_iterations}
\end{figure}

@@

%Estimators are evaluated based on the bias and variance properties of their estimates. 
%The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. 
%Due to the stochastic nature of simulation process, results of repeated experiments are normally preferred.

The performance of speckle filters are normally evaluated based on a few criteria \citep{Nyoungui_2002_IntlJRemoteSense}.
The most widely used criteria is speckle suppression, 
  which is often evaluated over homogeneous area.
The other important criteria include radiometric preservation, something undeniably desirable in the filtered output.
In practical terms, the most common usage of speckle filtered imagery include target and feature detection and classification.
In this section, the use of the ROC curve and the area under it as the statistical evidence of separability between target and clutter PDFs is briefly explored.

The performance of the FMLE filter is evaluated both qualitatively against real
images and quantitatively via simulated experiments. 
Over homogeneous regions, the speckle suppression power is
evaluated by measuring the ubiquitous MSE on simulated and truth-grounded experiments. 
The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available computational power, is sufficiently large.

For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as
statistical evidence for better performance in the subsequent tasks of target detection
and surface classification. 
Experiments confirm the power of FMLE filters in various
heterogeneously simulated areas. 
A good correlation between the MSE and the AUC index is also exhibited. 
The result suggests that lower MSE achievable by FMLE filters does lead to better performance in the subsequent tasks of target detection and classification.
Let us start with a qualitative visual evaluation of the speckle filter on real-captured images.

%We highlight the use of the ROC curve and the area under it as the statistical evidence of separability between target and clutter PDFs.
%We then show that lower MSE achievable by FMLE filters does lead to better performance in the subsequent tasks of target detection and classification.
%As is customary, we start by an visual evaluation of the filter on real-life images.
%We start with visual evaluation of the filters on real-life images.

The filters are applied to a SLC RadarSat 2 image covering the Muda Merbok area of Malaysia.
Fig. \ref{fig:fmle.real.images} shows the patches of original and filtered images of both natural and urban landscape.
The filtering effects are clearly visible.
Apparently the second iteration outputs appears much better than the initial application.
Furthermore, they offer roughly the same level of speckle suppression power in comparison to that of boxcar filter.

\afterpage{\clearpage}

\begin{figure}
\centering  
      \begin{tabular}[h]{c}
	\subfloat[Original]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter0.made.eps} 
		 \label{fig:fmle.natural.incl.iter0}
	} \hfill
	\subfloat[Boxcar]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/boxcar.natural.3x3.made.eps} 
		 \label{fig:boxcar.natural}
	}\\
	\subfloat[FMLE incl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter1.made.eps} 
		 \label{fig:fmle.natural.incl.iter1}
	} \hfill
	\subfloat[FMLE incl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter2.made.eps} 
		 \label{fig:fmle.natural.incl.iter2}
	} \\
	\subfloat[FMLE excl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.excl.iter1.made.eps} 
		 \label{fig:fmle.natural.excl.iter1}
	} \hfill
	\subfloat[FMLE excl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.excl.iter2.made.eps} 
		 \label{fig:fmle.natural.excl.iter2}
	} 
	\end{tabular}
\caption{Qualitative Evaluation of FMLE filter on Real Life Scene of Natural Surface}
\label{fig:fmle.real.images}
\end{figure}

\begin{figure}
\centering  
      \begin{tabular}{c}
	\subfloat[Original]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.excl.iter0.made.eps} 
		 \label{fig:fmle.urban.excl.iter0}
	} \hfill
	\subfloat[Boxcar]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/boxcar.urban.3x3.made.eps} 
		 \label{fig:boxcar.urban}
	} \\
	\subfloat[FMLE incl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.incl.iter1.made.eps} 
		 \label{fig:fmle.urban.incl.iter1}
	} \hfill
	\subfloat[FMLE incl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.incl.iter2.made.eps} 
		 \label{fig:fmle.urban.incl.iter2}
	} \\ 
	\subfloat[FMLE excl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.excl.iter1.made.eps} 
		 \label{fig:fmle.urban.excl.iter1}
	} \hfill
	\subfloat[FMLE excl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.excl.iter2.made.eps} 
		 \label{fig:fmle.urban.excl.iter2}
	} 
	\end{tabular}
\caption{Qualitative Evaluation of FMLE filter on Real Life Scene of Urban Landscape}
\label{fig:fmle.real.images}
\end{figure}

We have found that variance in the log-transformed domain is related to the standard Equivalent Number of Look value.
Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002_721}, the formula is given as:
$MSE = \frac{1}{(ENL - 0.5)ln^2(2)}$.
%An experiment is carried out to 
Fig. \ref{fig:verify_MSE_as_perf_index} demonstrates the relationship.
The use of iterative Fuzzy MLE estimations allows further suppression of speckle.
This is illustrated with ``tighter'' distance histograms and reducing MSE, as plotted in Fig. \ref{fig:Homogeneous_Area}

\begin{figure}
\centering
 \epsfxsize=9cm
 \epsfysize=9cm
 \epsffile{images/verify_MSE_as_perf_index.made.eps}
 \caption{MSE in the log-transformed domain is related to the ENL index}
 \label{fig:verify_MSE_as_perf_index}
\end{figure}

\begin{figure}
\centering
      \begin{tabular}[h]{c}
	\subfloat[MSE (incl, 3x3)]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/distance_pdf_simulation_iterative.incl.made.eps} 
		 \label{fig:distance_pdf_simulation_iterative.incl}  
	} \hfill
	\subfloat[MSE (excl, 3x3)]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/distance_pdf_simulation_iterative.excl.made.eps} 
		 \label{fig:distance_pdf_simulation_iterative.excl}
	} \\
	\subfloat[MSE (incl, 5x5)]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/distance_pdf_simulation_iterative.5x5.incl.made.eps} 
		 \label{fig:distance_pdf_simulation_iterative.incl.5x5}
	} \hfill
	\subfloat[MSE (excl, 5x5)]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/distance_pdf_simulation_iterative.5x5.excl.made.eps} 
		 \label{fig:distance_pdf_simulation_iterative.excl.5x5}
	}
     \end{tabular}
\caption{Homogeneous Area: MSE criteria and speckle suppression power of FMLE filters}
\label{fig:Homogeneous_Area}
\end{figure}
\afterpage{\clearpage}

The normal application after applying filters on SAR images is to detect the existence of certain target within its surrounding clutters or other similar classification / discrimination tasks.
The most common type of detector (or classifier) employs a threshold based approach in determing whether an abnormal value signifies the existence of a target.
The Receiver Characteristic Curve (ROC) and the area under it (AUC) is typically used to evaluate the detectability of target features \citep{Mazurowski_2009_IJCNN}.

It is normally claimed that applying speckle filters increases the performance of subsequent target detection tasks.
The following experiment illustrates this point.
In this experiment, we apply a simple 3x3 boxcar filter to two different homogeneous and SLC noise corrupted scenes that are known to be 3dB apart.
And then the histograms as well as the resulting ROC curve are plotted between the pairs of target and background histogram for both cases of unfiltered and filtered data.
We noted that the ROC curve for the histograms in original domain matches perfectly with ROC for the histograms in the log-transformed domain (see Fig. \ref{fig:PDF_Discriminality}), as expected from theory.

%\afterpage{\clearpage}

\begin{figure}
\centering
      \begin{tabular}[h]{c}
 	\subfloat[SLC Intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/illustrate_ROC_curve.pdf.s.made.eps} 
		 \label{fig:illustrate_ROC_curve.pdf.s.made.eps}
	} \hfill
	\subfloat[9-Look Intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/illustrate_ROC_curve.pdf.m.made.eps} 
		 \label{fig:illustrate_ROC_curve.pdf.m.made.eps}
	} \\
 	\subfloat[SLC log-intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/log_illustrate_ROC_curve.pdf.s.made.eps} 
		 \label{fig:log_illustrate_ROC_curve.pdf.s.made.eps}
	} \hfill
	\subfloat[9-Look log-intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/log_illustrate_ROC_curve.pdf.m.made.eps} 
		 \label{fig:log_illustrate_ROC_curve.pdf.m.made.eps}
	}
   \end{tabular}
\caption{Histogram Discriminality and the ROC Curve}
\label{fig:PDF_Discriminality}
\end{figure}

%\subfloat[Invariant ROC Curve]{
%\afterpage{\clearpage}
\begin{figure}
\centering  
 \epsfxsize=6cm
 \epsfysize=6cm
 \epsffile{images/log_illustrate_ROC_curve.made.eps} 
 \label{fig:illustrate_ROC_curve.roc}
 \caption{Invariant ROC Curve}
\end{figure}

The most common types of target to be detected in image processing are point targets, line targets, and edge targets.
The detectability of these targets are measured using the AUC index which is tabulated against the MSE.
Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of FMLE filters for heterogenous regions.
Aapparently the fMLE filters have better performance than boxcar filters.
Also noticeable is the correlation between MSE and the Area Under the ROC curve criteria, 
  which is an interesting phenomena that will be investigated further in the next section.
%Even though the relationship is probably not linear,
%  the correlation between MSE and Area Under the ROC curve (AUC) is apparent,
%Also FMLE filters apparently have better performance than boxcar filters.

\begin{figure}
\begin{minipage}[c]{0.48\textwidth}
%\captionsetup[subfigure]{labelformat=empty}
%\subfloat[]{%
%\captionsetup[subfigure]{labelformat=parens}
%\begin{figure}
%\centering
	\subfloat[Point Target]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/641bcaad-f54b-4bb6-8d10-77784da522a5.made.eps} 
		 \label{fig:point_target_pattern}
	}
	\subfloat[Edge]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/c5124949-1228-4749-a99e-caf9430e400a.made.eps} 
		 \label{fig:edge_pattern}
	}\\
	\subfloat[Line]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/a2e330a8-3deb-4328-94d8-d18c43e4f7a1.made.eps} 
		 \label{fig:line_pattern}
	}
	\subfloat[Dotted Pattern]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/38e79d4c-af61-4b1f-acc2-528ecedb96a7.made.eps} 
		 \label{fig:dotted_pattern}
	}
%\caption{Simulated Heterogeneous Patterns}
%\label{fig:distance_pdf_simulation_iterative}
%\end{figure}
\end{minipage}
%} & 
\begin{minipage}[c]{0.4\textwidth}
%\captionsetup[subfigure]{labelformat=empty}
%\subfloat[]{%
%\captionsetup[subfigure]{labelformat=parens}
%\begin{table}
%\centering
  \footnotesize
\begin{tabular}{|l|l|l|l|}
\hline
Scene 				& Filter 						& MSE 	& AUC \\
\hline
Point Target 	& FMLE (incl, 3x3) 	& 1.38	& 0.901 \\
Point Target 	& FMLE (excl, 3x3) 	& 1.47	& 0.893 \\
Point Target 	& boxcar (3x3) 			& 1.56	& 0.826 \\
Point Target 	& boxcar (5x5) 			& 2.67	& 0.502 \\
\hline
Edge 	& FMLE (incl, 3x3) 	& 0.68	& 0.969 \\
Edge 	& FMLE (excl, 3x3) 	& 0.73	& 0.964 \\
Edge 	& boxcar (3x3) 			& 1.03	& 0.942 \\
Edge 	& boxcar (5x5) 			& 1.51	& 0.934 \\
\hline
Line 	& FMLE (incl, 3x3) 	& 1.89	& 0.791 \\
Line 	& FMLE (excl, 3x3) 	& 2.02	& 0.767 \\
Line 	& boxcar (3x3) 			& 2.27	& 0.658 \\
Line 	& boxcar (5x5) 			& 2.88	& 0.375 \\
\hline
Dotted 			& FMLE (incl, 3x3) 	& 2.28	& 0.639 \\
Dotted 			& FMLE (excl, 3x3) 	& 2.32	& 0.621 \\
Dotted 			& boxcar (3x3) 			& 2.92	& 0.431 \\
Dotted 			& boxcar (5x5) 			& 3.35	& 0.382 \\
\hline
\end{tabular}
%\caption{The MSE \& ROC indices are correlated}
%\end{table}
\end{minipage}
%}
%\end{tabular}
\caption{Heterogeneous Patterns: MSE criteria and FMLE performance}
\label{fig:Heterogeneous_Patterns}
\end{figure}
\afterpage{\clearpage}

%The log-transformed domain provides a consistent sense of distance.
%By embracing a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes use of this consistency.
%Experimental results suggest that the estimator's output also exhibits this consistency property, which allows recursive application of the filter discussed above.
%
%The performance of the filter is evaluated both qualitatively against real images and quantitatively via simulated experiments.
%The speckle suppression power is evaluated by measuring the ubiquitous MSE on simulated and perfectly homogeneous truth-grounded experiments.
%The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available computational power, is sufficiently large.
%
%For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as statistical evidence for better performance in the subsequent tasks of target detection and surface classification.
%Experiments confirm the power of FMLE filters in various heterogeneously simulated areas.
%They also exhibit good correlation between the MSE and the AUC index.

The nature of SAR speckle is stochastic. 
The speckle filtering problem has been casted into a statistical estimation theory framework. 
Speckle filtering, by and large, means the removal of stochastic component in SAR images. 
Log-transformation is shown to provide homoskedasticity in statistical models. 
Using speckle filtering as an applicative example, these homoskedastic features are shown to be useful. %here to improve speckle-filtering.

The log-transformed domain provides a consistent sense of distance. By embracing
a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes
use of this consistency. Experimental results suggest that the estimator’s output also
exhibits this consistency property, which allows recursive application of the filter discussed above.

The speckle filtering technique proposed here has been shown to work for single-look SAR images. 
Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations. 
The fMLE approach is developed from an easy to understand winner-take-all kMLE clustering approach. %to a more fuzzy probabilistic clustering algorithm. 
With the fuzziness be taken to a new level, fuzzy probabilistic speckle filters which requires no clustering have been specified and designed.

%The nature of SAR speckle is stochastic. 
%The speckle filtering problem has been casted into a statistical estimation theory framework. 
%Speckle filtering, by and large, means the removal of stochastic component in SAR images. 
%Various negative effects of heteroskedasticity are discussed. 
%Log-transformation is shown to provide homoskedasticity in statistical models. 
%Using speckle filtering as an applicative example, these homoskedastic features are shown to be useful. %here to improve speckle-filtering.
%
%The speckle filtering technique proposed here has been shown to work for single-look SAR images. 
%Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations. 
%The filter is developed from an easy to understand winner-take-all clustering approach. %to a more fuzzy probabilistic clustering algorithm. 
%Should the fuzziness be taken to a new level, an optimal fuzzy probabilistic filter which requires no clustering may be specified and designed.

@@

@@

\subsubsection{ Estimating ENL from the log-variance index in homogeneous areas }
\label{sec:homogeneous_theoretical}
